Critical assessment of Linear-Response Excitations in Molecular system\\ or \\ On the Localization of the Linear-Response excitations in Open Systems

### 2017-12-17 LRDraft.tex
update

>>>>

We are interested in determining the time evolution of an eigenstate of $\hnot$ under the action of the perturbation $\hone{t}$ in the linear 
response regime. A proper statement of the problem requires the specification of the way in which the perturbation is switched on.
Possible choice of the switching on protocol are, for instance, the \emph{adiabatic limit} and the \emph{sudden limit} case. In the first
case the perturbation is switched on at $t_0=-\infty$, but the intrinsic time structure of $\hone{}$ is modified by the damping function 
$e^{-\eta_a |t|}$. In the second protocol the perturbation is abruptly switched on at the finite time $t_0$, so that the time structure of
$\hone{}$ is multiplied times the $\theta$-function $\theta(t-t_0)$.

It is possible to write:
\be \lb{ketTimeEvol3} 
\ket{\psi_p(t)} = e^{-\ii E_p t}\left( \identity - \ii \op A(t_0,t)  \right)\ket{\psi_p} \; ,
\ee
where: 
\be
\op A(t_0,t) = \intdef{t_0}{t}{t'} \op{U}_0(t-t') \hone{t'} \op{U}_0(t'-t)
\ee
we can write:
\be
\op A(t) = \intdef{-\infty}{\infty}{t'} \op{U}^{-}_0(t-t') \Phi^{a.l,s.l}(t') \op{U}^{+}_0(t'-t)
\ee
where:
\be
\Phi^{a.l.}(t) = e^{-\eta_a |t|} \hone{t} \;, \qq
\Phi^{s.l.}(t) = \theta(t-t_0) \hone{t}
\ee
